Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/discussions.tex

\paragraph{Memory buffer size scalings}~Thm.~\ref{th:cont-params} is stated for
transitions sampled sequentially from a fixed infinite size sequence. In practice,
transitions are sampled from a memory buffer, to prevent excessive correlations.
The memory buffer used is a fixed size circular buffer, filled
with samples from a single infinite exploratory trajectory. In
our experiments, the same buffer size is used for all time discretization. When
$\deltat$ goes to $0$, this corresponds to learning nearly online on the
infinite sequence, since the buffer will only contain examples that are very
close temporally to the end of the sequence in physical time. \TODO{this
contradicts the use of the buffer against correlations} While the resulting
algorithm converges to a continuous time limit, in the strictest sense it is not
time discretization invariant, as the freshness of samples in the buffer will
vary with the time discretization.
A different choice would be to scale the size of the buffer by a factor of
$\frac{1}{\deltat}$. This would amount to always learning on the same physical time interval of
the trajectory. Our theoretical analysis does not cover this case.

\paragraph{Near continuous time reinforcement learning and RMSprop}~RMSprop~\cite{rmsprop}
estimates a batched version of the second momentum of gradients using moving
averages, and divides gradient steps by the square root of this estimate. In
deterministic environments, gradient noise typically scales as $\bigO(1)$ in
term of $\deltat$, as seen in Eq.~\eqref{eq:approx_bellman_A}.  Consequently, RMSprop
preconditioning have no effect on the order of magnitude of required learning
rates. However, in near continuous stochastic environments, as in
Eq.~\ref{eq:sde}, variance of the gradient noise typically scales as
$\bigO\left(\frac{1}{\deltat}\right)$. If batch size does not depend on
$\deltat$, RMSprop preconditioning thus multiplies gradients by a factor $\bigO(\sqrt{\deltat})$,
and learning rates need only be scaled as $\alpha \sqrt{\deltat}$ instead of
$\alpha \deltat$.

>>>>

\paragraph{Memory buffer size scalings}~Thm.~\ref{th:cont-params} is stated for
transitions sampled sequentially from a fixed infinite size sequence. In practice,
transitions are sampled from a memory buffer, to prevent excessive correlations.
The memory buffer used is a fixed size circular buffer, filled
with samples from a single infinite exploratory trajectory. In
our experiments, the same buffer size is used for all time discretization. When
$\deltat$ goes to $0$, this corresponds to learning nearly online on the
infinite sequence, since the buffer will only contain examples that are very
close temporally to the end of the sequence in physical time. \TODO{this
contradicts the use of the buffer against correlations} While the resulting
algorithm converges to a continuous time limit, in the strictest sense it is not
time discretization invariant, as the freshness of samples in the buffer will
vary with the time discretization.
A different choice would be to scale the size of the buffer by a factor of
$\frac{1}{\deltat}$. This would amount to always learning on the same physical time interval of
the trajectory. Our theoretical analysis does not cover this case.
\TODO{a bit too many details here?}

\paragraph{Near continuous time reinforcement learning and RMSprop.} RMSprop~\cite{rmsprop}
estimates a batched version of the second moment of gradients via moving
averages, and divides gradient steps by the square root of this estimate.
This may interact with the learning rate scaling discussed above. In
deterministic environments, gradient noise typically scales as $\bigO(1)$ in
term of $\deltat$, as seen in \eqref{eq:approx_bellman_A}.  In that case, RMSprop
preconditioning has no effect on the suitable order of magnitude for learning
rates. However, in near continuous \emph{stochastic} environments, as in
Eq.~\ref{eq:sde}, variance of the gradient noise typically scales as
$\bigO\left(\frac{1}{\deltat}\right)$. If batch size does not depend on
$\deltat$, RMSprop preconditioning thus multiplies gradients by a factor $\bigO(\sqrt{\deltat})$,
and learning rates need only be scaled as $\alpha \sqrt{\deltat}$ instead of
$\alpha \deltat$.
